A content-sensitive framework for modeling episodic memory reveals event-like structure in naturalistic experience, recall, and neural processing

### 2019-08-29 paper/main.tex
added ref to new supplemental figures

\newcommand{\topicopt}{S1}
\newcommand{\topics}{S2}
\newcommand{\featureimportance}{S3}
% \newcommand{\listlearning}{S4}
\newcommand{\corrmats}{S4}
\newcommand{\matchmats}{S5}
\newcommand{\wasserstein}{S6}

@@

\begin{figure}[tp]
\centering
\includegraphics[width=\textwidth]{figs/eventseg}
\caption{\small \textbf{Modelling naturalistic stimuli and recalls.} All panels: darker colors indicate greater values; range: [0, 1].  \textbf{A.} Topic vectors ($K = 100$) for each of the 1976 video timepoints.  \textbf{B.} Timepoint-by-timepoint correlation matrix of the topic vectors displayed in Panel A.  Event boundaries detected by the HMM are denoted in yellow (36 events detected).  \textbf{C.} Average topic vectors for each of the 36 video events. \textbf{D.} Topic vectors for each of 294 sentences spoken by an example participant while recalling the video, resampled to match the timseries of the video.  \textbf{E.} Timepoint-by-timepoint correlation matrix of the topic vectors displayed in Panel D. Event boundaries detected by the HMM are denoted in yellow (37 events detected).  \textbf{F.} Average topic vectors for each of the 37 recalled events from the example participant.  \textbf{G.} Correlations between the topic vectors for every pair of video events (Panel C) and recalled events (from the example participant; Panel F).  For similar plots for all participants see Figure~\matchmats.  \textbf{H.} Average correlations between each pair of video events and recalled events (across all 17 participants).  To create the figure, each recalled event was assigned to the video event with the most correlated topic vector (yellow boxes in panels G and H).  The heat maps in each panel were created using \texttt{Seaborn}~\citep{WaskEtal16}.}
\label{fig:model}
\end{figure}

@@

We used an optimization procedure to select the appropriate $K$ for each topic proportions matrix.  Specifically, we computed (for each matrix)
\[
  \argmax_K \left[\frac{a}{b} - \frac{K}{\alpha}\right],
\]
where $a$ was the average correlation between the topic vectors of timepoints within the same state; $b$ was the average correlation between the topic vectors of timepoints within \textit{different} states; and $\alpha$ was a regularization parameter that we set to 5 times the window length (i.e., 250 scenes for the video topic trajectory and 50 sentences for the recall topic trajectories).  Figure~\ref{fig:model}B displays the event boundaries returned for the video, and Figure~\corrmats~displays the event boundaries returned for each participant's recalls.  After obtaining these event boundaries, we created stable estimates of each topic proportions matrix by averaging the topic vectors within each event.  This yielded a number-of-events by number-of-topics matrix for the video and recalls from each participant.

>>>>

\newcommand{\topicopt}{S1}
\newcommand{\topics}{S2}
\newcommand{\featureimportance}{S3}
% \newcommand{\listlearning}{S4}
\newcommand{\corrmats}{S4}
\newcommand{\matchmats}{S5}
\newcommand{\wasserstein}{S6}
\newcommand{\kcorrs}{S7}
\newcommand{\kopt}{S8}

@@

\begin{figure}[tp]
\centering
\includegraphics[width=\textwidth]{figs/eventseg}
\caption{\small \textbf{Modelling naturalistic stimuli and recalls.} All panels: darker colors indicate greater values; range: [0, 1].  \textbf{A.} Topic vectors ($K = 100$) for each of the 1976 video timepoints.  \textbf{B.} Timepoint-by-timepoint correlation matrix of the topic vectors displayed in Panel A.  Event boundaries detected by the HMM are denoted in yellow (36 events detected).  \textbf{C.} Average topic vectors for each of the 36 video events. \textbf{D.} Topic vectors for each of 252 sentences spoken by an example participant while recalling the video, resampled to match the timseries of the video.  \textbf{E.} Timepoint-by-timepoint correlation matrix of the topic vectors displayed in Panel D. Event boundaries detected by the HMM are denoted in yellow (29 events detected).  \textbf{F.} Average topic vectors for each of the 29 recalled events from the example participant.  \textbf{G.} Correlations between the topic vectors for every pair of video events (Panel C) and recalled events (from the example participant; Panel F).  For similar plots for all participants see Figure~\matchmats.  \textbf{H.} Average correlations between each pair of video events and recalled events (across all 17 participants).  To create the figure, each recalled event was assigned to the video event with the most correlated topic vector (yellow boxes in panels G and H).  The heat maps in each panel were created using \texttt{Seaborn}~\citep{WaskEtal16}.}
\label{fig:model}
\end{figure}

@@

We used an optimization procedure to select the appropriate $K$ for each topic proportions matrix.  Specifically, we computed (for each matrix)
\[
  \argmax_K \left[\frac{a}{b} - \frac{K}{\alpha}\right],
\]
where $a$ was the average correlation between the topic vectors of timepoints within the same state; $b$ was the average correlation between the topic vectors of timepoints within \textit{different} states; and $\alpha$ was a regularization parameter that we set to 5 times the window length (i.e., 250 scenes for the video topic trajectory and 50 sentences for the recall topic trajectories).  Figure~\ref{fig:model}B displays the event boundaries returned for the video, and Figure~\corrmats~displays the event boundaries returned for each participant's recalls (see Figs.~\kcorrs, \kopt~for the optimization functions for the video and recalls).  After obtaining these event boundaries, we created stable estimates of each topic proportions matrix by averaging the topic vectors within each event.  This yielded a number-of-events by number-of-topics matrix for the video and recalls from each participant.
